Multi-product Batch Processing Time Maximization Problem

### 2023-07-14 (2023) Fraga et al.tex
updating files

%\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
%             city={Caruaru},
%             postcode={55014-900},
%             state={PE},
%             country={Brasil}}

@@

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution method for solving this problem.

@@

\section{Analytical solution}
\label{sec:analyticalSol}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r}
$i$ & 1 & 2 & total \\
\cline {1-4} \\
$\textrm{p}_i$ & 60 & 40 & \\
$\textrm{UD}_i$ & 1000 & 500 & \\
$\textrm{UO}_i$ & 600 & 600 & 1000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
\cline {1-4} \\
& & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTMP 001}
\label{tab:MBPTMP001}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r r}
$i$ & 1 & 2 & 3 & total \\
\cline {1-5} \\
$\textrm{p}_i$ & 60 & 40 & 50 \\
$\textrm{UD}_i$ & 1000 & 500 & 800 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
\cline {1-5} \\
& & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTMP 002}
\label{tab:MBPTMP002}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{small}
\begin{tabular}[c]{c r r r r r r r r r r r }
$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
\cline {1-12} \\
$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
\cline {1-12} \\
& & & & & & & & & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MBPTMP 003}
\label{tab:MBPTMP003}
\end{small}
\end{center}
\end{table}

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and the analytical method}
\label{tab:results}
\end{footnotesize}
\end{center}
\end{table}

>>>>

\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
\ead{tatiana.balbi@ufpe.br}
\cortext[cor1]{corresponding author}

\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
\ead{italo_ruan_@hotmail.com}

\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
\ead{regilda.smenezes@ufpe.br}

\affiliation[label1]{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
             city={Caruaru},
             postcode={55014-900},
             state={PE},
             country={Brasil}}

@@

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.

@@

\section{Fraga's analytical solution}
\label{sec:analyticalSol}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r}
$i$ & 1 & 2 & total \\
\cline {1-4} \\
$\textrm{p}_i$ & 60 & 40 & \\
$\textrm{UD}_i$ & 1000 & 500 & \\
$\textrm{UO}_i$ & 600 & 600 & 1000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
\cline {1-4} \\
& & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MPBPTMP 001}
\label{tab:MBPTMP001}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}[c]{c r r r r}
$i$ & 1 & 2 & 3 & total \\
\cline {1-5} \\
$\textrm{p}_i$ & 60 & 40 & 50 \\
$\textrm{UD}_i$ & 1000 & 500 & 800 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
\cline {1-5} \\
& & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MPBPTMP 002}
\label{tab:MBPTMP002}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{small}
\begin{tabular}[c]{c r r r r r r r r r r r }
$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
\cline {1-12} \\
$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
\cline {1-12} \\
& & & & & & & & & & $\textrm{Z}$ & 100 \\
\end{tabular}
\caption{Benchmark MPBPTMP 003}
\label{tab:MBPTMP003}
\end{small}
\end{center}
\end{table}

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MPBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
MPBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MPBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
RMPBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
RMPBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
RMPBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
RMPBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
RMPBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and the analytical method}
\label{tab:results}
\end{footnotesize}
\end{center}
\end{table}
